The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
social scale v2

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  github_document
  # bookdown::pdf_document2:
  #   number_sections: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

In general, individuals in multilayer networks became more connected as a function of social scale, however, this relationship varied by habitat type and season. As social scale increased, connective redundancy increased rapidly when groups were formed based on ~100m threshold, followed by a plateau and slight decrease at higher thresholds, presumably due to an increase in summer forest degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not change for any habitat types or seasons, which suggests habitat-by-season layers captured most, if not all, of the potential connections and individual would have across all networks (Figure 3c). Finally, somewhat predictably, graph strength for winter networks increased up to ~100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d).

* increasing graph strength consistent with increasing strength in winter

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  #github_document
  bookdown::pdf_document2:
     number_sections: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

In general, individuals in multilayer networks became more connected as a function of social scale, however, this relationship varied by habitat type and season. As social scale increased, connective redundancy increased rapidly when groups were formed based on ~100m threshold, followed by a plateau and slight decrease at higher thresholds, presumably due to an increase in summer forest degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not change for any habitat types or seasons, which suggests habitat-by-season layers captured most, if not all, of the potential connections and individual would have across all networks (Figure 3c). Finally, somewhat predictably, graph strength for winter networks increased up to ~100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d).  Taken together, these results suggest the optimal social scale at which groups should be assigned is likely somewhere between ~20-100m based on the rate at which network metrics stabilized. For ungulates, groups are often assigned based on 50m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar quantities of data, ~50m is likely an ideal social scale for generating social networks in caribou and similar species.
